\SW: II. New Gravitational Lens Candidates from the CFHTLS Discovered through Citizen Science

### 2015-05-09 doc/sw-cfhtls.tex
incorporated AV's edits and Phil's correct until Section 3.3  (corresp. 211fe65)

In order to perform a blind lens search over the entire \cfhtls
WIDE, we present the volunteers with cutouts of images selected
from the survey region. We briefly describe the image presentation here
for completeness; more information can be found in \PaperOne. We use
the $g$, $r$ and $i$-band imaging from \cfhtls which are most useful for
visual identification of lenses.  We made color composite images using
the publicly-available code, \humvi\footnote{The open source  color image
composition code used in this work is available from
\texttt{http://github.com/drphilmarshall/HumVI}} following the
prescription of \citet{Lupton2004}. The color scales were chosen to
maximize the contrast between faint extended objects. These parameters
were then fixed during the production of all the tiles, in order to allow
straightforward comparison between one image and another, and for
intuition to be built up about the appearance of stars and galaxies
across the survey.

@@

The simulated lens sample, although realistic, is not perfect, due to
the simplicity of the lensing models and our limited understanding of
the uncertainties in the model parameters. Comments from citizen
scientists were very helpful in order to sort some of these failures.
Here, we describe some of the cases or aspects in which the simulations
were known to be unrealistic. The fraction of such unrealistic simulations in the 
simulated sample is small (roughly 5 percent)\footnote{This estimate is
based on the number of \#simfail tags from \Talk, the discussion forum.}.

>>>>

In order to perform a blind lens search over the entire \cfhtls
WIDE, we present the volunteers with cutouts of images selected
from the survey region. We briefly describe the image presentation here
for completeness; more information can be found in \PaperOne. We use
the $g$, $r$ and $i$-band imaging from \cfhtls which are most useful for
visual identification of lenses.  We made color composite images using
the publicly-available code, \humvi\footnote{The open source  color image
composition code used in this work is available from
\texttt{http://github.com/drphilmarshall/HumVI}} following the
prescription of \citet{Lupton2004}. The color scales were chosen to
maximize the contrast between faint extended objects and bright early
type galaxies. These parameters
were then fixed during the production of all the tiles, in order to allow
straightforward comparison between one image and another, and for
intuition to be built up about the appearance of stars and galaxies
across the survey.

@@

The simulated lens sample, although realistic, is not perfect, due to
the simplicity of the lensing models and our limited understanding of
the uncertainties in the model parameters. Comments from citizen
scientists were very helpful in order to sort some of these failures.
Here, we describe some of the cases or aspects in which the simulations
were known to be unrealistic. The fraction of such unrealistic cases in the 
simulated sample is small (roughly 5 percent)\footnote{This estimate is
based on the number of \#simfail tags from \Talk, the discussion forum.}.
